---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Calistoga&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Montserrat:ital,wght@0,100..900;1,100..900&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Shadows+Into+Light&display=swap');

body {
  font-family: 'Montserrat';
  background-color: #ffedfc;
  color: #005ea0;
}

h1    {
  font-family: "Calistoga", serif;
  font-weight: bold;
}

h2    {
  font-family: "Calistoga", serif;
  font-weight: bold;
  background-color: #8ddcc5;
  text-align: center;
}

h3    {
  text-align: center;
}

h4    {
  text-align: center;
  font-family: "Shadows Into Light", cursive;
  font-weight: bold;
  font-size: 20px;
}

p   {
  font-family: 'Montserrat';
  text-align: center;
}

```

## What are my listening habits on spotify?

I used the survey project to better understand my listening habits on spotify. I classified each time I listened to music as a 'session' and answered questions about each listening session that I had. Variables that I recorded in my survey included the duration of listening, the reason for listening, the enjoyment ranking, whether I had a favourite song from that session, did I start by shuffling or choosing a specific song, did I listen to a playlist or listen from another source ect. The survey gave me insights into why and how I listen to music. 

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRzPeDfeBK7dfTaUOQCgW5-5Ns-hlTGi9O2A6D1Waech1ZyfAg7gO4CVRFaqCvoSgQLPuAIBdoa-dAw/pub?gid=1796407430&single=true&output=csv")

#renaming variables
latest_data <- logged_data %>%
    rename(timestamp = 1,
           duration = 2,
           reason = 3,
           source = 4,
           new_songs = 5,
           rating = 6,
           favourite = 7,
           start = 8,
           select_song = 9,
           select_reason = 10)

max_rate <- latest_data %>%
              select(rating) %>% max()

min_rate <- latest_data %>%
              select(rating) %>% min()
rate <- paste("The maximum enjoyment rating of a session was", max_rate, "out of 9. The minimum enjoyment rating of a session was", min_rate, "out of 9.")

new_max <- latest_data %>%
              select(new_songs) %>% max()

songs_new <- paste("the maximum amount of new songs that I listened to in one session was", new_max,". This must have been on a day that I was listening to spotify generated playlists.")



```
There were some interesting results regarding the enjoyment ratings of each session. `r rate` I also tracked the amount of new songs I listened to per session. Most of the time I listened to 0 new songs. However, `r songs_new`

Some of the data of my listening habits can be seen in the following figures.
      
```{r fig.width = 7, fig.height = 4}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRzPeDfeBK7dfTaUOQCgW5-5Ns-hlTGi9O2A6D1Waech1ZyfAg7gO4CVRFaqCvoSgQLPuAIBdoa-dAw/pub?gid=1796407430&single=true&output=csv")

#renaming variables
latest_data <- logged_data %>%
    rename(timestamp = 1,
           duration = 2,
           reason = 3,
           source = 4,
           new_songs = 5,
           rating = 6,
           favourite = 7,
           start = 8,
           select_song = 9,
           select_reason = 10)

ggplot(data = latest_data) +
           geom_bar(aes(x = rating,
                      fill = reason)) +
      labs(title = "Is it the Music or the Act?",
       subtitle = "Comparing the enjoyment rating of listening to music with the reason for listening",
       caption = "Source: Rosa Mitchell's Listening Survey Data",
       x = "Enjoyment Rating (1 is did not enjoy, 9 is very much enjoyed)",
       y = "Frequency of rating") +
  scale_fill_discrete(name = "Reason for listening")

```



```{r fig.width = 7, fig.height = 4}
ggplot(data = latest_data) +
              geom_bar(aes(y = reason, fill = source))+
  labs(title = "The Reason vs The Source",
       subtitle = "Does the reason for listening dictate the source of the music?",
       caption = "Source: Rosa Mitchell's Listening Survey Data",
       x = "Frequency",
       y = "Reason for Listening") +
  scale_fill_discrete(name = "Source of music")

```



```{r fig.width = 7, fig.height = 4}
ggplot(data = latest_data) +
            geom_bar(aes(y = favourite), 
                    fill = "#ffb6f7") + #changing the colour 
       labs(title = "How often was a single was song my 'favourite'?",
       subtitle = "The songs I listed as my favourite from a listening session 
and how often they appeared",
       caption = "Source: Rosa Mitchell's Listening Survey Data",
       x = "Name of the song and the artist",
       y = "Frequency")


```


